Clone Overflow: \\ An empirical study of online code clone

### 2016-09-23 latex/stackoverflow.tex
Latest version

@@

\title{Code Overflow: \\
	An empirical study of online code reuse}
\maketitle

\section*{Raw statistics}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\begin{table*}[h]
	\centering
	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} 
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ 
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
		\hline
		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total  	& 654 	& 24,929 	& -- 	& --	& 1,175 & 16,957,362 & --	& --	& 985 	& 105,118 	& --	& --	& 12,084	& 113,557,298 & --		& -- \\
		Mean  	& --	& 38 		& 7.54 	& 0.27 	& --	& 14,444 	& 4.80 	& 0.28 	& --	& 107 		& 9.52 	& 0.25 	& -- 		& 9,397 	& 5.21 		& 0.20 \\
		Std Dev. & --  	& 87 		& 3.21 	& 0.22 	& --	& 281,747 	& 1.22 	& 0.18 	& --	& 198 		& 3.07 	& 0.18 	& --		& 12,098 	& 1.73 		& 0.16 \\
		Max  	& --	& 551 		& 49.00 & 0.94 	& --	& 9,599,676 & 18.00 & 0.89 	& --	& 1,792 	& 39.00 & 0.80 	& --		& 227,077 	& 44.00 	& 0.86 \\
		Min  	& --	& 1 		& 5.00 	& 0.01 	& --	& 1 		& 4.00 	& 0.02 	& --	& 1 		& 7.00 	& 0.02 	& --		& 1 		& 3.00 		& 0.01 \\
		Median  & --	& 3 		& 7.00 	& 0.23 	& --	& 22 		& 5.00 & 0.24 	& --	& 15 		& 8.00 	& 0.19 	& --		& 6,105 	& 5.00 		& 0.15 \\
		Mode  	& --	& 1 		& 7.00 	& 0.25 	& --	& 1 		& 4.00 	& 0.50 	& --	& 1 		& 8.00 	& 0.53 	& --		& 1 		& 4.00 		& 0.33 \\
		\hline
	\end{tabular} %
}
\end{table*}

@@

	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}

@@

	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}

@@

%\begin{table}[H]
%	\centering
%	\caption{Qualitas projects (2016-08-16) successfully analysed by Simian and NiCad}
%	\label{tab:projects_missing_new}
%	\begin{tabular}{r|r|r|r}
%		\hline
%		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
%		44	& 40 & 44 & 34 \\
%		\hline
%		& \textit{4 clustering failed} &  & \textit{6 clustering failed} \\
%		\hline
%		& jboss (wildfly) &	& ArgoUML \\
%		& db-derby 	&  &  db-derby \\
%		& hadoop 	& &  checkstyle \\
%		& hibernate & &  cayenne \\
%		&  			& &  geotools \\
%		&  			& &  jena \\
%		\hline
%		& \textit{no renaming failed} & &  \textit{4 renaming failed} \\
%		\hline
%		&			& & Vuze \\
%		&			& & hadoop \\
%		&			& & hibernate \\
%		&			& & jboss (wildfly) \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{table}[H]
	\centering
	\caption{Distribution of clone pairs reported based on \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c|}{Qualitas-\textit{O}} & \multicolumn{2}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,640 \\ 
		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 416 \\ 
		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
		\textit{fse13} 	& \textit{fse13} 	& 1,388 & 10,206 & 1,170 & 6,690 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,386 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 10,879 \\
		\hline
	\end{tabular}
\end{table}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
%	\label{fig:venn4_pairs_good}
%\end{figure}

%\begin{table}[H]
%	\centering
%	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
%	\label{t_agreed_ok_clone_pairs}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure}

%\begin{table}[H]
%	\centering
%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
%	\label{t_dup_agreed_ok_clone_pairs}
%	\begin{tabular}{l|r|r|r|r|r}
%		\hline
%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
%		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
%		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
%		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
%		\hline
%		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
%	\label{fig:venn4_pairs}
%\end{figure}

%The statistics of the results from Simian and NiCad are shown in Table \ref{t_agreed_good_clone_pairs_new}, \ref{t_agreed_ok_clone_pairs_new}, and Figure \ref{fig:venn4_pairs_good_new}, and \ref{fig:venn4_pairs_ok_new}.
%
%\begin{table}[H]
%	\centering
%	\caption{1,170 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,170 are unique)}
%	\label{t_agreed_good_clone_pairs_new}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 0 & 0 \\ 
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 0 & 1,170 \\ 
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good_new}
		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_new_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok_new}
		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_new_ok}
	\end{minipage}
\end{figure}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good_new}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
%	\label{fig:venn4_pairs_good_new}
%\end{figure}

%\begin{table}[H]
%	\centering
%	\caption{13,733 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
%	\label{t_agreed_ok_clone_pairs_new}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ 
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 6604 & 23 \\
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 416 & 6690 \\
%		\hline
%	\end{tabular}
%\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (13,386 are different, 347 are duplicates)}
%	\label{t_dup_agreed_ok_clone_pairs}
%	\begin{tabular}{l|r|r|r|r|r}
%		\hline
%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		$S_dN_d$ & 6267	& 337	& 0		& 	0	&  6604 \\
%		$S_dN_f$ & 337 	& 79	& 0 	&  	0	&  416 \\ 
%		$S_fN_d$ & 0 	& 0		& 13 	&   10	&  23 \\
%		$S_fN_f$ & 0 	& 0 	& 10	&  	6680 &  6690 \\	
%		\hline
%		Total 	 & 6604  & 416	& 23	& 6690	& 13733 \\
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok_new}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
%	\label{fig:venn4_pairs_ok_new}
%\end{figure}

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
\subsubsection{Qualitas Original (v. 2013-09-01r)}
\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}. We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 664 \textit{ok-match} pairs that were investigated. The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.

@@

\begin{table}[H]
	\centering
	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
	\label{tab:classification}
	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
		\hline
		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
		 & A & A' & B & C & D & E & F & Total 
		 & A & A' & B & C & D & E & F & Total \\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}} 
		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
		\hline
		\multirow{1}{*}{\textit{ok-match(0.7)}} 
		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
		\hline
		TP/FP
		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
		\hline
		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
		\hline
		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
		\hline
		Unique Q files & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
		\hline
	\end{tabular} 
\end{table}

@@

\subsubsection{Qualitas New (v. 2016-08-05)}
We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

>>>>

\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}

@@

\title{Clone Overflow: \\
	An empirical study of online code clone}
\maketitle

\section*{Research Questions}
\begin{itemize}
	\item \textbf{RQ1 (online code clone):} \textit{can we find any reused source code fragments between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened or has been happening and at what scale.
	\item \textbf{RQ2 (Direction of online code clone flow):} \textit{in which direction source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both?
	\item \textbf{RQ3 (Online code clone classification):} \textit{what are categories of online code clone?} How and why did these online code clone happen?
	\item \textbf{RQ4 (Effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
\end{itemize}

\section*{Experimental Results}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\begin{table*}[h]
	\centering
	\caption{Qualitas-\textit{O} (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} 
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ 
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
		\hline
		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total  	& 654 	& 24,929 	& -- 	& --	& 1,175 & 16,957,362 & --	& --	& 985 	& 105,118 	& --	& --	& 12,084	& 113,557,298 & --		& -- \\
		Mean  	& --	& 38 		& 7.54 	& 0.27 	& --	& 14,444 	& 4.80 	& 0.28 	& --	& 107 		& 9.52 	& 0.25 	& -- 		& 9,397 	& 5.21 		& 0.20 \\
		Std Dev. & --  	& 87 		& 3.21 	& 0.22 	& --	& 281,747 	& 1.22 	& 0.18 	& --	& 198 		& 3.07 	& 0.18 	& --		& 12,098 	& 1.73 		& 0.16 \\
		Max  	& --	& 551 		& 49.00 & 0.94 	& --	& 9,599,676 & 18.00 & 0.89 	& --	& 1,792 	& 39.00 & 0.80 	& --		& 227,077 	& 44.00 	& 0.86 \\
		Min  	& --	& 1 		& 5.00 	& 0.01 	& --	& 1 		& 4.00 	& 0.02 	& --	& 1 		& 7.00 	& 0.02 	& --		& 1 		& 3.00 		& 0.01 \\
		Median  & --	& 3 		& 7.00 	& 0.23 	& --	& 22 		& 5.00 & 0.24 	& --	& 15 		& 8.00 	& 0.19 	& --		& 6,105 	& 5.00 		& 0.15 \\
		Mode  	& --	& 1 		& 7.00 	& 0.25 	& --	& 1 		& 4.00 	& 0.50 	& --	& 1 		& 8.00 	& 0.53 	& --		& 1 		& 4.00 		& 0.33 \\
		\hline
	\end{tabular} %
}
\end{table*}

@@

	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}

@@

	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of clone pairs reported based on \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c|}{Qualitas-\textit{O}} & \multicolumn{2}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,604 \\ 
		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 79 \\ 
		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
		\textit{fse13} 	& \textit{fse13} 	& 1,388 & 10,206 & 1,170 & 6,690 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,396 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 13,386 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good}
		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok}
		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure}

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_new}
		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_new_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_new}
		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_new_ok}
	\end{minipage}
\end{figure}

@@

\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
\begin{table}[H]
	\centering
	\caption{Classifications of clone creation}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table}

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}. We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 664 \textit{ok-match} pairs that were investigated. The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.

@@

\begin{table}[H]
	\centering
	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
	\label{tab:classification_good_o}
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & 5 & 5 & 4 & 4 & 26  & 6 & 1369 & 1401 & 56 & 416 & 31 & 1406 & 61 & 420 & 32 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 36  & 8 & 52 & 8 & 10 & 6 & 474 & 57 & 81 & 612 & 77 & 62 & 17 & 664 & 84 & 70 & 20 \\
		\hline
	\end{tabular} 
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
%	\label{tab:classification}
%	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
%		\hline
%		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
%		 & A & A' & B & C & D & E & F & Total 
%		 & A & A' & B & C & D & E & F & Total \\ 
%		\hline 
%		\multirow{1}{*}{\textit{good-match(0.7)}} 
%		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
%		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
%		\hline
%		\multirow{1}{*}{\textit{ok-match(0.7)}} 
%		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
%		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
%		\hline
%		TP/FP
%		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
%		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
%		\hline
%		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%		Unique Q projects & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%	\end{tabular} 
%\end{table}

@@

\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table \ref{tab:classification_good_n}.
